\documentclass[11pt, a4paper, final]{article}
\usepackage{tmh}
\usepackage{bbm}
\renewcommand{\labelenumi}{\roman{enumi}}
\renewcommand{\phi}{\varphi}

\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\Dt}{\Delta t}
\newcommand{\Dv}{\Delta v}
\newcommand{\Dx}{\Delta x}
\newcommand{\dx}{\dif x}
\newcommand{\dt}{\dif t}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[scaled]{helvet}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\usepackage{showkeys}

\title{{\huge Numerical Methods for an Interacting Particle System}}
\author{Thomas M. Hodgson\\ \vspace{0.5cm} Maxwell Institute Graduate School}
\date{\today}
\newcommand\testname{Acknowledgements}
\newenvironment{acknowledge}
{\renewcommand\abstractname{\testname}\begin{abstract}}
    {\end{abstract}}

\begin{document}
	\maketitle
    \thispagestyle{empty}
	\newpage
	\tableofcontents
	\listoffigures
	\newpage
    \begin{abstract}
        We describe and analyse a Vicsek-type model from both the kinetic and particle views. Techniques are then presented which allow the numerical approximation of these models before being applied and compared.
    \end{abstract}
    \begin{acknowledge}
        My thanks to Seb Strug\footnote{\url{https://github.com/SebStrug}} for introducing me to the Seaborn and Pandas Python libraries which have been used for many of the figures in this report. Thanks also to Dr. Charlotte Desvages for teaching a great Python course which lead to me switching allegiance from MATLAB.
    \end{acknowledge}
      \newpage 
	\section{Introduction}\label{sec:introduction}
        \input{Chapters/introduction}
       
	\section{The Model}\label{sec:model}
        \input{Chapters/model1}      
	\section{Dynamics}\label{sec:dynamics}
        \input{Chapters/dynamics1}
        
   	\section{Numerical Methods}\label{sec:numericalmethods}
        \input{Chapters/numericalmethods}
 
    \section{Applying the Numerical Scheme}\label{sec:application}
        \input{Chapters/application}
        
    \section{Discussion}\label{sec:discussion}
        \input{Chapters/conclusion}

    \bibliographystyle{abbrv}
    \bibliography{whales.bib}
    \appendix
    \section{Implementation}\label{app:code}
    All the numerical schemes described above were implemented in Python 3. Before doing this project I had very little knowledge of Python beyond the basics, and a passing knowledge of MATLAB. As part of this project I have written a Python package to solve the toy problems, as well as the one-dimensional kinetic model and particle system. There is also a set of functions designed to produce animations and plots of the solutions. All of these are available under an MIT License and described further at 
    \begin{center}\url{https://github.com/Tom271/InteractingParticleSystems}\end{center}
    \texttt{Project Supplement.ipynb} shows the basic use of all the methods and how to produce plots and animations of the solution. The algorithms and functions themselves lie in the \texttt{src} folder as \texttt{.py} files, meaning they can be downloaded and used without Jupyter being installed.
\end{document}