We now have enough techniques to begin solving the kinetic model. Consider the space-homogeneous evolution given by \eqref{eq:spacehomPDE}, that is
    \begin{equation}
    \partial_t f_t(v) = \partial_v vf_t(v) - \partial_v G(\langle w \rangle_{f_t})f_t(v) + \sigma \partial_{vv} f_t(v).
    \end{equation}
    Using the methods developed in the previous section, we are now able to solve this system numerically. As when solving the heat equation, a zero boundary condition shall be enforced. This is valid as we know that the stationary distributions are Gaussian and centred at $-1,0,+1$. The boundary $L$ can then be chosen depending on the the diffusion so that almost no mass is contained beyond the boundary. For example if $\sigma = 1$, the mass contained beyond $L=5$ is of the order $10^{-5}$. 
    
    Simpson's rule will be used as a quick way to approximate the integral within the herding coefficient. To differentiate between the integral and its approximation, we write \(\langle w\rangle_{F^n}\). Below is the scheme when both the herding coefficient and the velocity are positive, using a finite difference scheme with a CN discretisation for the diffusive term and an upwind method for the damping and herding terms.
    \begin{equation*}
    \begin{split}
    \frac{F_j^{n+1} - F_j^n}{\Delta t} = 	-G(\langle w\rangle_{F^n})\left[ \frac{F^n_{j+1} - F^n_{j}}{\Delta v}\right] &+\left[ \frac{v_{j}F^n_{j} - v_{j-1}F^n_{j-1}}{\Delta v}\right]\\ &+ \frac{\sigma}{2}\left[ \frac{F^{n+1}_{j+1} - 2F^{n+1}_j + F^{n+1}_{j-1}}{(\Delta v)^2} + \frac{F^{n}_{j+1} - 2F^{n}_j + F^{n}_{j-1}}{(\Delta v)^2}\right] 	 
    \end{split}
    \end{equation*}
    
    +++Pictures, moments converging, error (in moments too?) in particular, mass loss? -> compare conservative methods i.e. fin vol +++
    \subsection{Space Heterogeneous}
    +++ phi = 1 still, moving in space. Animations/diagrams showing Leb in space. +++
    